\section{Emerging Topics: Evaluation \& Business Models}

\subsection*{Strategy \& Program Evaluation}
\begin{itemize}
    \item \textbf{Difference-in-Differences (Diff-in-Diff):} A statistical technique used to
          evaluate the effect of a specific intervention or program (e.g., Lean
          Manufacturing implementation, Work From Home policies) by comparing changes in
          outcomes over time between a treatment group and a control group.
    \item \textbf{Calculation:}
          \begin{enumerate}
              \item $\text{Diff}_1 = \text{After} - \text{Before (Treatment)}$
              \item $\text{Diff}_2 = \text{After} - \text{Before (Control)}$
              \item $\text{Diff-in-Diff} = \text{Diff}_1 - \text{Diff}_2$
          \end{enumerate}
\end{itemize}

\subsection*{Business Model Canvas}
\begin{itemize}
    \item \textbf{Definition:} The way a company creates and captures value, acting as the bridge
          between a firm's internal competencies and its customers. It helps solve
          complex strategic problems with many interdependencies.
    \item \textbf{Company \& Partners (Left Side):}
          \begin{itemize}
              \item \textit{Key Partners:} Network of suppliers and partners.
              \item \textit{Key Activities:} Most important actions a company must take to operate
                    successfully.
              \item \textit{Key Resources:} Most important assets required to make the business model work.
              \item \textit{Cost Structure:} All costs incurred to operate the business model.
          \end{itemize}
    \item \textbf{Customer (Right Side):}
          \begin{itemize}
              \item \textit{Value Proposition:} The bundle of products and services that create value for a
                    specific segment.
              \item \textit{Customer Relationships:} Types of relationships established with specific
                    segments.
              \item \textit{Channels:} How a company communicates with and reaches its segments to deliver
                    the value proposition.
              \item \textit{Customer Segments:} The different groups of people or organizations an
                    enterprise aims to reach.
              \item \textit{Revenue Streams:} The cash generated from each customer segment.
          \end{itemize}
\end{itemize}

\subsection*{Financial Analysis}
\begin{itemize}
    \item \textbf{Fixed Cost ($FC$):} One-time investments (e.g., plants, machinery, R\&D,
          advertising).
    \item \textbf{Unit Cost ($UC$):} Cost of developing one product or serving one customer
          (e.g., cost of materials used).
    \item \textbf{Break-Even Point ($Q$):} The exact number of units you need to sell to cover
          all costs (where Total Revenue = Total Cost).
    \item \textbf{Formula:} $$Price \times Q = UC \times Q + FC$$
\end{itemize}